---
title: "Getting the most out of R"
subtitle: "Physalia Courses"  
author: 
  - "Luis D. Verde Arregoitia"
date: 'February 2021'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
library(fontawesome)
library(gt)
library(dplyr)
library(tidyr)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF",
  inverse_background_color = "#8d99ae",
  base_font_size = "25px",
  text_font_size=  "1.25rem",
  link_decoration = "underline dotted red",
  code_font_size = "1.25rem",
  code_inline_color= "#003049",
  code_inline_background_color = "#FFFCFE",
  blockquote_left_border_color = "#003049"
  )

```

```{r xaringan-tachyons, echo=FALSE}
library(xaringanExtra)
xaringanExtra::use_tachyons()
```

```{r xaringan-panelset, echo=FALSE, eval=TRUE}
xaringanExtra::use_panelset()
```

```{r xaringan-animate-all, echo=FALSE, eval=TRUE}
xaringanExtra::use_animate_all("fade")
```

```{r xaringan-extra-styles, eval=TRUE, echo=FALSE}
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,     
)
```

```{css, echo = F}
.dk-section-title {
box-shadow: inset 0 0 0 1000px rgba(0,0,0,0.5);
}

.dk-section-title h1 {
  color: #f3f3f3;
  font-size: 100px;
  line-height: 1;
}

```

## Thursday - Overcoming errors and getting unstuck


- Friendly online resources

- Building web searches to solve common problems

- Identifying the best solutions

- Creating reproducible examples with the 📦 {`reprex`} package 

---

- Friendly online resources

StackOverflow
Twitter
github issues (closed and open)
RStudio Community


---
 Getting help
 
---

Etiquette


---
.center[
<blockquote class="twitter-tweet" data-conversation="none" data-dnt="true"><p lang="en" dir="ltr">If you are looking for help with an <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> problem, I recommend that you<br>🎯do *not* email an individual author or OSS maintainer<br>🎯create a reprex demonstrating your problem (naturally none in this email)<br>🎯post on a public forum like RStudio Community or Stack Overflow</p>&mdash; Julia Silge (@juliasilge) <a href="https://twitter.com/juliasilge/status/1477778836968259587?ref_src=twsrc%5Etfw">January 2, 2022</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script> 
]

--- 
 Reproducible examples
 
 
---
- Building web searches to solve common problems

- Identifying the best solutions

- Creating reproducible examples with the 📦 {`reprex`} package 
